---
title: "Visualization1"
author: "Chirag Shah"
date: '2018-09-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggridges)
```

Cache because you don't want to be pulling data from the external server for everytime
```{r data_import, cache = TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

##Start a plot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

only gives a blank graph with the axes.

New plot 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

now data is added to the axes we had before 

```{r}
weather_df %>%
  filter(name == "CentralPark_NY") %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Can also save plots from previous lecture 


##More plot options 

add an aesthetic

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

add a geom
add a smooth line in the graph 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE) ##se=false gets rid of confidence band
```
alpha makes the points and more transparent 

add some options
#now aestheitic mapping is applied to entire plot (globally) for every geometry

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE)
```

```{r}
 ##separate panels for each name
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

can also use geom_line to connect the dots

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_line() +
  facet_grid(. ~ name)
```

##Univariate plots

histograms

```{r}
ggplot(weather_df, aes(x = tmax)) +
  geom_histogram()
```
only needs x variable because y axis will always be count 

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) +
  geom_histogram() +
  facet_grid(~ name)
```

Density plots

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) +
  geom_density(alpha = 0.5) +
  facet_grid(~ name)
```

Box plots

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_boxplot()
```

Violin plots

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4)
```

violin plot shows the shape of the distribution that the box plot does not

```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5) ##font size stays the same but the figure size is bigger
```

Embedding plots in an R Markdown document can also take a while to get used to, because there are several things to adjust. First is the size of the figure created by R, which is controlled using two of the three chunk options fig.width, fig.height, and fig.asp. I prefer a common width and plots that are a little wider than they are tall, so I set options to fig.width = 6 and fig.asp = .6. Second is the size of the figure inserted into your document, which is controlled using out.width or out.height. I like to have a little padding around the sides of my figures, so I set out.width = "90%". I do all this by including the following in a code snippet at the ##outset of my R Markdown documents.

## put this is a code chunk at the very begining
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

